\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 appendix.tex
appendix

============================================================================
EMSOFT 2017 Reviews for Submission 159
============================================================================

@@

============================================================================
                            REVIEWER 1
============================================================================

---------------------------------------------------------------------------
Reviewer's Scores
---------------------------------------------------------------------------

@@

---------------------------------------------------------------------------
Comments
---------------------------------------------------------------------------

@@

   Is this why the PWA transition system characterizes states by a valuation
   function v and not simply as tuples? If yes, how will this work? I do not
   understand why you have a valuation function when the system only has one
   variable (x).
   ============
   [TODO]
   ============
============================================================================
                            REVIEWER 2
============================================================================

---------------------------------------------------------------------------
Reviewer's Scores
---------------------------------------------------------------------------

@@

---------------------------------------------------------------------------
Comments
---------------------------------------------------------------------------

@@

============================================================================
                            REVIEWER 3
============================================================================

---------------------------------------------------------------------------
Reviewer's Scores
---------------------------------------------------------------------------

@@

---------------------------------------------------------------------------
Comments
---------------------------------------------------------------------------

The paper presents a method for falsifying safety properties of hybrid systems.
The method first constructs a relational abstraction of the system (which is
considered as a black box) from a set of simulation traces. The relations in
the abstraction are affine with uncertainty. The approach is quite interesting,
however the examples used for demonstration are unfortunately not black boxes,
although these examples are treated as black boxes, since it would be of great
interest to show its usefulness for complex models for which traditional
verification tools cannot be applied. A comparison with S3CAM is interesting,
but is less informative than a comparison with simulation-based validation
tools.
I also recommend using relations more complex than affine, such as polynomial,
for which Z3 can be used (nonlinear relations may reduce the number of
hyper-rectangles).

The method is of heuristic nature and thus convincing experimental results
would be needed. The paper compares with previous work (S3CAM) using a similar
approach. This approach has been tested on more real-life examples from
automative control. I am wondering why there are no comparisons on these
examples.

============================================================================
                            REVIEWER 4
============================================================================

---------------------------------------------------------------------------
Reviewer's Scores
---------------------------------------------------------------------------

@@

============================================================================
                            REVIEWER 5
============================================================================

---------------------------------------------------------------------------
Reviewer's Scores
---------------------------------------------------------------------------

>>>>

\obeyspaces
\obeylines
======================================
EMSOFT 2017 Reviews for Submission 159
======================================

@@

=====================================
                            REVIEWER 1
=====================================

----------------------------------
Reviewer's Scores
---------------------------------

@@

------------------------------------
Comments
-----------------------------------

@@

   Is this why the PWA transition system characterizes states by a valuation
   function v and not simply as tuples? If yes, how will this work? I do not
   understand why you have a valuation function when the system only has one
   variable (x).
   ============
   [TODO]
   ============
======================================
                            REVIEWER 2
======================================

--------------------------------------
Reviewer's Scores
--------------------------------------

@@

--------------------------------------
Comments
--------------------------------------

@@

======================================
                            REVIEWER 3
======================================

--------------------------------------
Reviewer's Scores
--------------------------------------

@@

--------------------------------------
Comments
--------------------------------------

A comparison with S3CAM is interesting, but is less informative than a
comparison with simulation-based validation tools.

I also recommend using relations more complex than affine, such as
polynomial, for which Z3 can be used (nonlinear relations may reduce
the number of hyper-rectangles).

======================================
                            REVIEWER 4
======================================

--------------------------------------
Reviewer's Scores
--------------------------------------

@@

======================================
                            REVIEWER 5
======================================

--------------------------------------
Reviewer's Scores
--------------------------------------
